Reconstructing the neutron-star equation of state with gravitational-wave detectors from a realistic population of inspiralling binary neutron stars

### 2014-08-18 paper.tex
Some comments on Section V

In this Section we characterize the ability of the aLIGO--aVirgo network to measure the EOS from a population of BNS inspiral events. We use the zero detuned-high laser power (broadband) configuration~\cite{LIGOnoise} which represents the design sensitivity that may be achieved for the aLIGO detectors by 2019~\cite{AasiAbadieAbbott2013}. The design sensitivity of aVirgo has slightly higher noise and may be achieved by 2021~\cite{AasiAbadieAbbott2013}. For the results here we use the same broadband aLIGO configuration for all three detectors and note that the differences have only a minor quantitative impact on the results.

@@

For the population presented here, we sampled a year of inspiral events using the ``realistic'' event rate of 100~MWEG$^{-1}$ Myr$^{-1}$. \red{[[Is there a missing piece here? Did you draw from a Poisson distribution, or use exactly 100?]]} The masses for each event were sampled as discussed above, and position and orientation were sampled uniformly. For the three-detector network, this resulted in 121 events with \textit{network} $\text{SNR} \ge 8$ \red{[[Why is this so much larger than $40\times\sqrt{3}$?]]}. We performed parameter estimation for the 50 loudest sources with network SNR that ranged from 64.1 down to 10.7. Seven of these sources had network $\text{SNR} > 20$.

>>>>

In this Section we characterize the ability of the aLIGO--aVirgo network to measure the EOS from a population of BNS inspiral events. We use the zero detuned-high laser power (broadband) configuration~\cite{LIGOnoise} which represents the design sensitivity that may be achieved for the aLIGO detectors by 2019~\cite{AasiAbadieAbbott2013}. The design sensitivity of aVirgo has slightly higher noise and may be achieved by 2021~\cite{AasiAbadieAbbott2013}. For the results here we use the same broadband aLIGO configuration for all three detectors and note that the differences have only a minor quantitative impact on the results \les{(This is not what I did.  I used the parameterized Advanced Virgo PSD from Eq. 6 of 1202.4031 for Virgo.  Does that mess up the consistency of any of our results?)}{}.

@@

For the population presented here, \les{we simulated a BNS population equivalent to the ``realistic'' one from \cite{LIGORate2010}.  We populated a spherical volume of $r=819.6$ Mpc and density of 0.0116 MWEG Mpc$^{-3}$ with BNS events inspiralling at a rate of 100 MWEG$^{-1}$ Myr$^{-1}$.  This resulted in
\begin{eqnarray}
N_{\rm BNS}&=&\frac{3}{4}\pi(819.6\mbox{ Mpc})\\
\nonumber
&&\times(0.0116\mbox{ MWEG Mpc}^{-3})\\
\nonumber
&&\times(100\mbox{ MWEG}^{-1}\mbox{ Myr}^{-1})\\
\nonumber
&=&2,675\mbox{ yr}^{-1}.
\end{eqnarray}
Since this is a Poisson process, the number of BNS systems per year used in our simulation was drawn from a Poisson distribution about 2,675 yr$^{-1}$, and this was 2,698 yr$^{-1}$.}{we sampled a year of inspiral events using the ``realistic'' event rate of 100~MWEG$^{-1}$ Myr$^{-1}$.} \red{[[Is there a missing piece here? Did you draw from a Poisson distribution, or use exactly 100?]]}\les{(I did draw from a Poisson distribution, as I've now described above)}{} The masses for each event were sampled \les{uniformly between [1.2M$_\odot$,1.6M$_\odot$]}{as discussed above}, and position and orientation were sampled uniformly \les{within the volume}{}.  \les{Of the 2,698 BNS systems simulated, $\sim$120 of them had a network SNR $\ge$ 8 and $\sim$30 had a network SNR $\ge$ 12.}{ For the three-detector network, this resulted in 121 events with \textit{network} $\text{SNR} \ge 8$} \red{[[Why is this so much larger than $40\times\sqrt{3}$?]]}\les{(The horizon distance will scale by $\sqrt{3}$, not the number of detected inspirals.  So, if you take $445\mbox{ Mpc }\times\sqrt{3}=770\mbox{ Mpc}$ and calculate the number of detectable inspirals consistent with the Rates paper, you get $\sim$190.  We get a different number because we have a slightly different horizon distance from our three detector network where we actually calculate SNR as opposed to using that 2.26$^{-3}$ factor, which is really only a good approximation for the single detector case.)}{}. We performed parameter estimation for the \les{20}{50} loudest sources with network SNR that ranged from 64.1 down to \les{13.7}{10.7}\les{(I think we should use the network SNR calculated by LALInference instead of the network SNR calculated when I simulated the population.  I used TaylorT4 with $f_{\rm low}=10$ Hz to simulate the population, which is not exactly what was used in the injection.  If you agree, the loudest signal have network SNR = 63.7 and the 20$^{\rm th}$ loudest has network SNR = 13.6.)}{}. Seven of these sources had network $\text{SNR} > 20$ \les{(If we go with the LALInference network SNR calculations, which I think we should, technically only 6 have net SNR $>$ 20 b/c the seventh has net SNR = 19.95.)}{}.
